Bayesian model in JAGS

### 2023-01-26 3_JAGS_Bayesian_model/Jags_Bayesian_model.Rmd
correct minor mistakes

######## sample for posterior distribution ##########
censor_model_sample <- coda.samples(censor_model_jags,
                            c("beta0","beta1",
                            "lambda1","lambda2",
                            "lambda3","inv_var"),
                             100000,thin=20)
```

@@

>>>>

######## sample for posterior distribution ##########
censor_model_sample <- coda.samples(censor_model_jags,
                            c("beta0","beta1",
                            "lambda1","lambda2",
                            "inv_var"),
                             100000,thin=20)
```

@@

## Same process to sample posteriors of spatiotemporal model

```{r, message=FALSE, eval=FALSE}
## loading data from the working directory
spatial_model_data <- readRDS("./spatial_model_data.rds")

### Read in the model file using the jags.model function ##
spatial_model_jags <- jags.model(textConnection(censor_spatial_model),
                     data=spatial_model_data,n.chains = 4)

############ burn-in period ############
update(spatial_model_jags,10000)

######## sample for posterior distribution ##########
spatial_model_sample <- coda.samples(spatial_model_jags,
                            c("beta0","beta1",
                            "inv_var",
                            "b0","b1","b2"),
                             100000,thin=20)
```
